Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-28 paper.qmd
caption for fig 2

<!-- XXX SHOW THE S-CURVE DATA WITH THE TRUE MODEL OVERLAID HERE, BEFORE THE NLDR VIEWS. -->

@@

Three views of the true model in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>). 
:::

>>>>

@@

Three views of the true model (grey points and lines) in $2\text{-}D$ projections from $7\text{-}D$, for the S-curve data (purple points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>). 
:::
